---
title: 'DATA 607 Assignment #3'
author: "Tyler Baker"
date: "9/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(stringr)
```

## Exercise 1

Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r exercise #1}
#There should be three majors that belong to this subset.

majors<- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv")
#read the csv file.
str(majors)
desired_majors <- grep("DATA|STATISTICS", majors$Major, value=TRUE)
desired_majors
```

## Exercise 2

Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r exercise 2}
ugly_sting <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"'
better_string <- str_remove_all(ugly_sting, "[^[:alnum:]\\W]")
writeLines(better_string)
#Only thing left to do is to add a comma after every second quotation.
```

# Exercise 3
Describe, in words, what these expressions will match:

(.)\1\1
```{r}
library(htmlwidgets)
test <- c("a", "abab","aabb", "abba", "abracadabra", "a\1\1", "aaaaaaa", "aabbaa")
str_view_all(test, "(.)\1\1")
```

This expression searches for any character that is followed by the characters "\1\1".

"(.)(.)\\2\\1"
```{r}
str_view_all(test, "(.)(.)\\2\\1")
```

This expression searches for strings that contain the following format: char(a)char(b)char(b)char(a)

(..)\1
```{r}
str_view_all(test, "(..)\1")
```

This expression looks for any two characters that are followed by the literal characters \1.

"(.).\\1.\\1"
```{r}
str_view_all(test, "(.).\\1.\\1")
```

This expression searches for any string of the form a[]a[]a, where a can be any character, and inside the brackets must be seperate characters.

"(.)(.)(.).*\\3\\2\\1"
```{r}
str_view_all(test, "(.)(.)(.).*\\3\\2\\1")
```

This expression I believe takes any three characters abc and searches for strings that have the form abc[]cba. Where the bracket can be any character.

#Exercise 4

construct regular expressions to match words that:

Start and end with the same character.
```{r}
str_view_all(test, "^(.).*\\1$")
```
Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r}
test_new <- c("church", "eleven")
str_view_all(test_new, "(..).*\\1")
```
Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
```{r}
str_view_all(test_new, "(.).*\\1.*\\1")
```
